Judging domestic cooking ability: repeated incomplete rank observations

### 2020-08-24 inst/cook_repeated.Rmd
consistentify

```{r data}
cooking_table <- as.matrix(read.table("cooking_weekly.txt", header=TRUE))
cooking_table
```
Thus from the first row we find that one judge considered Lesley to be
fourth best, Alice third, Zac second and Annabel best (this must have
been Robin: no-one is allowed to vote for themselves and a zero means
no vote).  This is the transpose of an order table such as
`skating.txt`.  In this context a zero contains no information (unlike
the formula 1 tables in which zeros signify did not finish).  Document
`curling.Rmd` contains a discussion and here we will use the same
method.  First we will consider the support function for the first row only:

@@

```{r}
jj <- cooking_table[1,]
H_row1 <- order_obs(hyper2(pnames=colnames(cooking_table)),jj[jj>0])
H_row1
```

@@

```{r}
p1 <- rdirichlet(1,dirichlet(rep(10,5)))
# Now create p2 which is the same but competitor 1 is stronger:
p2 <- p1
p2[1] <- p2[1] + 0.1     # person 1 becomes stronger...
p2[-1] <- p2[-1] - 0.1/4 # ...and everyone else becomes weaker

loglik(indep(p1),H_row1)
loglik(indep(p2),H_row1)
```

but more generally:

```{r}
(p <- rdirichlet(1,dirichlet(rep(1,5))))
evaluate(brackets(H_row1), powers(H_row1), probs=p)
evaluate(brackets(H_row1), powers(H_row1), probs=p*4)
```

@@

```{r}
H <- hyper2(pnames=colnames(cooking_table))

for(i in seq_len(nrow(cooking_table))){  # iterate over rows
    x <- cooking_table[i,] 
    names(x) <- colnames(cooking_table)
    H %<>% order_obs(x[x>0])
}
H
```

@@

```{r}
cooking_table <-
	as.matrix(read.table("cooking_weekly.txt", header=TRUE))
cooking_table <- cooking_table[rowSums(cooking_table==0)==1,]
boys <-c("robin","zac")
girls <- c("lesley","alice","annabel")
cooks <- colnames(cooking_table)
P <- hyper2(pnames=c(cooks,"boy","girl"))
P0 <- hyper2(pnames=cooks)
for(i in seq_len(nrow(cooking_table))){  # iterate over rows
    x <- cooking_table[i,] 
	print(x)
	if(sum(x==0)>1){break}
    names(x) <- cooks
	if(names(x[x==0]) %in% boys){  # if the voter is a boy
		x <- x[x>0]  # remove the voter
		Pjj <- order_obs(P0,x) # order statistic
		Pjj %<>% pwa(names(x)[names(x) %in% boys], chameleon="boy")
		pnames(Pjj) <- c(cooks,"boy","girl")
	} else if (names(x[x==0]) %in% girls){ # voter a girl
		x <- x[x>0]
		Pjj <- order_obs(P0,x)
		Pjj %<>% pwa(names(x)[names(x) %in% girls], chameleon="girl")
		pnames(Pjj) <- c(cooks,"boy","girl")
	} else {
		stop()
	}
    P <- P + Pjj
}
x
Pjj
P
maxp(P)
```

>>>>

```{r data}
cooking_table <- as.matrix(read.table("cooking_weekly.txt", header=TRUE))
head(cooking_table)
tail(cooking_table)
```
Thus from the first row we find that one judge considered Lesley to be
fourth best, Alice third, Zac second and Annabel best (this must have
been Robin: no-one is allowed to vote for themselves and a zero means
no vote).  This is the transpose of an order table such as
`skating.txt`.  In this context a zero contains no information (unlike
the formula 1 tables in which zeros signify did not finish).  Document
`curling.Rmd` contains a discussion and here we will use the same
method.  First we will consider the support function for the first row only:

@@

```{r}
(day1 <- cooking_table[1,])
H_row1 <- rank_likelihood(day1[day1>0])
```

@@

```{r}
p <- c(0.3,0.2,0.1,0.3)
# Now create p2 which is the same but competitor 1 is stronger:
p2 <- p
alpha <- 1.3
beta <- (1-alpha*p[1])/(1-p[1])
p2[1] <- p2[1]*alpha   # person 1 becomes stronger...
p2[-1] <- p2[-1]*beta  # ...and everyone else becomes weaker

loglik(indep(p),H_row1)
loglik(indep(p2),H_row1)
```

@@

```{r}
H <- hyper2()

for(i in seq_len(nrow(cooking_table))){  # iterate over rows
jj <- cooking_table[i,] 
    H <- H + rank_likelihood(jj[jj>0])
}
H
```

@@

```{r,cache=TRUE}
cooking_table <-
	as.matrix(read.table("cooking_weekly.txt", header=TRUE))
cooking_table <- cooking_table[rowSums(cooking_table==0)==1,]
boys <-c("robin","zac")
girls <- c("lesley","alice","annabel")
cooks <- colnames(cooking_table)
P <- hyper2()
P0 <- hyper2()
for(i in seq_len(nrow(cooking_table))){  # iterate over rows
    x <- cooking_table[i,] 
	if(sum(x==0)>1){break}
    names(x) <- cooks
	if(names(x[x==0]) %in% boys){  # if the voter is a boy
		x <- x[x>0]  # remove the voter
		Pjj <- pwa(rank_likelihood(x),names(x)[names(x) %in% boys], chameleon="boy")
	} else if (names(x[x==0]) %in% girls){ # voter a girl
		x <- x[x>0]
		Pjj <- pwa(rank_likelihood(x),names(x)[names(x) %in% girls], chameleon="girl")
	} else {
		stop()
	}
    P <- P + Pjj
}
mP <- maxp(P)
```

```{r}
mP
pie(mP)
```

Now test whether the girls preferentially vote:

```{r,cache=TRUE}
specificp.gt.test(P,"girl",0)
```
